---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Tidy tools

<!-- badges: start -->
<!-- badges: end -->

Notes and live code a 2-day workshop on "tidy tools". This workshop is (mostly) coded live. You can see the scripts I work from in [`scripts/`](scripts/), but I recommending not reading too far ahead because you'll find answers to some of the exercises, and you'll learn more if you try to work through them first.

Slides:

* [Intro to package development](1-intro.pdf)
* [Testing](2-testing.pdf)
* [Sharing](3-sharing.pdf)

## Setup

```{r, echo = FALSE, include = FALSE}
deps <- unique(sort(renv::dependencies()$Package))
deps <- setdiff(deps, c(
  "ns", # created during class
  "rmarkdown", "knitr", # only needed for .Rmd
  "renv", # only needed for this block
  "itdepends", # not on CRAN
  "stats", # recommended
  tidyverse::tidyverse_packages(),
  NULL
))
install <- c(
  'install.packages(c("tidyverse", "devtools"))',
  paste0("install.packages(c(", paste0(encodeString(deps, quote = '"'), collapse = ", "), "))"),
  'devtools::install_github("r-lib/itdepends")'
)
```
```{r code = install, eval = FALSE}
```

```{r, eval = FALSE}
usethis::create_from_github("hadley/fordogs", fork = FALSE)
```


* When you're done, put a green post-it on your computer. 
* If you need help, put up a pink post-it.

