# Dependencies

```{r}
sd

x <- 1:10
sd(x)

var <- function(x) 100
var(x)
sd(x)
```
```{r}
my_sd <- function(x) sqrt(var(x))
my_sd(x)
```

## Scoping

```{r}
x <- 1
f <- function() {
  y <- 2
  z <- 2
  g <- function() {
    z <- 3
    c(x, y, z)
  }
  g()
}
f()
```

* What is an environment?
  * Where stuff lives
  * Set of bindings between names and object
  * Lookup table
  * Data structure powers scoping
* How is it different from a list?
  * Environments are unordered
  * x <- 1
  * x
  * Environments have parent

* What's the "default" environment?
* How can you see what's inside an environment?

```{r}
library(rlang)
env_print(globalenv())

rm(x)
env_print(globalenv())

rm(var, tb, f, my_sd, install_github)
env_print(globalenv())
```

## `find_env()`

```{r}
find_env <- function(name, env) { 
  if (identical(env, emptyenv())) {
    stop("Can't find `", name, "`", call. = FALSE)
  } else if (env_has(env, name)) {
    env
  } else {
    find_env(name, env_parent(env))
  }
}

x <- 1
find_env("x", globalenv())
find_env("c", globalenv())
find_env("asdfsd", globalenv())
```

```{r}
find_env("var", get_env(my_sd))
find_env("var", get_env(sd))
```

## Your turn

* `create_package("~/desktop/ns")`
* `use_mit_license()`
* `use_r("sd")`:

    ```{r}
    #' My standard deviation function
    #'
    #' @param x A numeric vector
    #' @param na.rm Remove missing values?
    #' @export
    my_sd <- function (x, na.rm = FALSE) {
      sqrt(var(x, na.rm = na.rm))
    }
    ```

* `devtools::check()`

## Using a function from another package

* `use_package("other-package")`
* Either `dplyr::mutate` or `@importFrom dplyr mutate`

* `@importFrom dplyr mutate` affects every function in your package
  * Slightly better to all import directives in one place
  * The place to put it is a package documentation file
  * `use_package_doc()`

* Avoid `@import dplyr`
  * Some exceptions: `@import rlang` ok, because rlang designed for it
  * `@import stringr` because all functions have `str_` prefix


* `@importFrom` is needed for infix functions, like `@importFrom magrittr %>%`
* If you also want the user of your package to have access to the pipe, call `use_pipe()` - this "re-exports" `%>%`

## Practice

* Put this in a package called counting
* Document it
* Get R CMD check passing

```{r}
my_count <- function(x) {
  count(data.frame(x = x), x, sort = TRUE)
}
```

## When to take a dependency?

**Brainstorm**: What are the costs and benefits of a taking a dependency?

Costs:
* Don't know the details
* Don't control the code (so update might break your code)
* Respect their license
* Download and install time
* No bragging rights

Benefits:
* Performance
* Not your problem
* Thought through more edge cases / exposed to more people
* Focus on your problem
* Don't know how to do it / too hard

**Your turn**: Compare and contrast dplyr with glue. Look at their CRAN pages - and see what you can quantify

* number of github issues: 24 (glue) vs 67 (dplyr)
* needed packags: 0 (glue) vs 13+ (dplyr)
* windows package size: 170 kb (glue) vs 3.2 mb (dplyr)
* install time: 3s (glue) vs 300s (dplyr)

```{r}
itdepends::dep_weight(c("dplyr", "glue"))
```

