## Motivation

```{r}
library(ggplot2)
library(dplyr)

# Create a local copy of first 10 rows of mtcars data frame
# We'll come back how you should store this later
mtcars <- data.frame(
  mpg = c(21, 21, 22.8, 21.4, 18.7, 18.1, 14.3, 24.4, 22.8, 19.2),
  cyl = c(6, 6, 4, 6, 8, 6, 8, 4, 4, 6),
  disp = c(160, 160, 108, 258, 360, 225, 360, 146.7, 140.8, 167.6),
  hp = c(110, 110, 93, 110, 175, 105, 245, 62, 95, 123),
  drat = c(3.9, 3.9, 3.85, 3.08, 3.15, 2.76, 3.21, 3.69, 3.92, 3.92),
  wt = c(2.62, 2.875, 2.32, 3.215, 3.44, 3.46, 3.57, 3.19, 3.15, 3.44),
  qsec = c(16.46, 17.02, 18.61, 19.44, 17.02, 20.22, 15.84, 20, 22.9, 18.3),
  vs = c(0, 0, 1, 1, 0, 1, 0, 1, 1, 1),
  am = c(1, 1, 1, 0, 0, 0, 0, 0, 0, 0),
  gear = c(4, 4, 4, 3, 3, 3, 3, 4, 4, 4),
  carb = c(4, 4, 1, 1, 2, 1, 4, 2, 2, 4)
)

# cyl_plot()
ggplot(mtcars) + 
  geom_bar(aes(cyl)) + 
  coord_flip()

# cyl_sum()
mtcars %>% 
  group_by(cyl) %>% 
  summarise(n = n(), mpg = mean(mpg))
```

* `create_package("~/desktop/tidytest")`
* `use_mit_license()` / `use_gpl3_license()`
* make two functions: `cyl_plot()` and `cyl_summary()`
* make it work - remember dependency stuff (`use_something()`, and `::`)
* get check passing as cleanly as you can

---

What did we do?

* Remove `library()` calls; and replace with calling `use_package()` once
* `use_pipe()` OR `@importFrom magrritr %>%` + `use_package(magrittr)`
* Resolve df-var vs env-var ambiguity by using `.data$`
* `@importFrom rlang .data` + `use_package("rlang")`

## Tidy evaluation

```{r}
library(tidyverse)

a <- 1
df <- data.frame(b = 1)

mutate(df, c = a + b)
ggplot(df, aes(a, b)) + geom_point()

n <- 2
ggplot(mtcars, aes(disp, mpg)) + 
  geom_point() + 
  geom_smooth(method = "lm", formula = y ~ splines::ns(x, df = n))
```

**Your turn**: Add this function to your package and get R CMD check passing:

```{r}
#' @importFrom rlang SOMETHING
diamonds_summary2 <- function(bins) {
  ggplot2::diamonds %>% 
    ggplot2::ggplot(ggplot2::aes(carat, price)) + 
    ggplot2::geom_hex(bins = bins)
}
```

