# Interface

<https://design.tidyverse.org>

```{r}
y <- sum(x)
```

Assuming this code works (with out errors or warnings):

* What do you know about `x`?
  * Numeric or logical vector (or matrix/array)
  
* What do you know about `y`?
  * Length 1
  * Numeric
  
```{r}
y <- sapply(x, f)
```

## What else compose the interface?

What are the properties of a function that define its interface? (There are at least 9)

* Name

* Inputs (arguments)
  * Names
  * Types (vector, scalar etc) 
  * Defaults
  * Model of evaluation (does it use tidy evaluation?)

* Output
  * Type
  * Visibility

* Side-effects
  * Saving a file to disk
  * Showing a plot
  * Printing in the console

* Errors/warnings/messages

```{r}
hidden <- function(x) invisible(x ^ 2)
hidden(100)
x <- hidden(100)
x

side_effect <- function(x) {
  
}
```

Digression about conflicted package - which I highly recommend.

## String functions

```{r, eval = FALSE}
strsplit(x, split, ...)
grep(pattern, x, value = FALSE, ...)
grepl(pattern, x, ...)
sub(pattern, replacement, x, ...)
gsub(pattern, replacement, x, ...)
regexpr(pattern, text, ...)
gregexpr(pattern, text, ...)
regexec(pattern, text, ...)
substr(x, start, stop)
nchar(x, type, ...)
```

What about the interface of these functions makes them to hard to use/remember?

* Names
  * Confusing
  * Don't have a common prefix
  * g should be a suffix

* Arguments
  * Order inconsistent
  * Character vector should come first
  * Names inconsistent (`x` and `text`; `pattern` and `split`)

* Output: `regexpr` not easily used with the other functions
  
* Packaging: no easy to find the complete collecitonx
  
```{r}
x <- c("abc", "bca", "dfaaa", "bc")
str(regexpr("a+", x))
```

### Names

```{r}
strsplit()           # str_split()
grep()               # str_which()
grep(value = TRUE)   # str_subset() - str_sub()
grepl()              # str_detect()
sub()                # str_replace()
gsub()               # str_replace_all()
```

```{r}
str_which()  # locations in the character vector

x <- c("apple", "banana", "lemon")
str_which(x, "a")

str_locate() # locations in the individual strings
str_locate(x, "a")
```

```{r}
str_SOMETHING_lgl() # str_detect
str_SOMETHING_int() # str_which
str_SOMETHING_chr() # str_subset

str_locate() # str_which
chr_locate() # str_locate
```

* Most functions should be verbs (exception is interfaces like ggplot2 where you're building up complex objects with nouns)

* Use prefixes to arrange families of related functions; use suffixes for variation on theme. Motivated by autocomplete

* Think a lot about names. Good name provdes mental hook that aids memory.

* BE CONSISTENT - pick one of snake_case and camelCase and use it!

**Your turn**: What stringr (and other tidyverse ) functions, don't follow these principles? Why not?

* `as.interval()`, `geom_point(na.rm = TRUE)`  - today would create `as_interval()`, `geom_point(na_rm = TRUE)`

(Aside: use `Ctrl + . ` to navigate between files and functions)

* `arrange()` - `arrange(df, desc(x))` 
   vs `arrange_asc(df, x)`; `arrange_desc(df, x)`
   `arrange(df, x, desc(y))`

* `left_join()`, `right_join()` -> should be
  `join_left()`, `join_right()`.

* `filter()`: keeping in or throwing out? 
  * `cleave()`, `

* UK vs US English - `scale_colour_gray()`
  * `summarise()` vs `summarize()`
  * `col`, or `stroke` / `fill`, `col1`, `col2`

## Arguments

* want argument names to be consistent. Both consistent style, and consistent names across functions.

* If the first argument is a data frame: `data`; if it's a vector call it `x`

**Your turn**: Can you divide these function arguments into functional groups?

```{r}
strsplit(x, split, fixed = TRUE)
grepl(pattern, x, fixed = TRUE, ignore.case = TRUE)
gsub(pattern, replacement, x, fixed = TRUE, ignore.case = TRUE)
gregexpr(pattern, text, fixed = TRUE)
substr(x, start, stop)
mutate(df, ...)
left_join(x, y, by = c("xyz", "def"))
str_detect(x, pattern, negate = TRUE) # !str_detect(x, pattern)
```

* Data: `x`, `df`, `y`, `text` - main vector argument

* Descriptors: `pattern`, `replacement`, `by`, `start`, `stop`

* Details: `fixed`, `ignore.case`, `negate` - control the detail of the algorithm. Almost always optional

Order arguments from most important to least important. And least important should have defaults. Putting the "data" first, ensures that it works with the pipe. And required arguments (no defaults), should come be optional arguments (with defaults).

When calling a function, you should always spell out name of details arguments; and don't use names for data arguments.

```{r}
mean(x, na.rm = TRUE)
mean(x = x, , TRUE)
mean(n = T, x)

str_replace_all(x, "[a-z]", "")
```

Sometimes can have one complicated argument or two simpler arguments:

```{r}
library(stringr)

hw <- "Hadley Wickham"
pos <- str_locate_all(hw, "[aeio]")[[1]]
str_sub(hw, pos[, 1], pos[, 2])
```

```{r}
grepl("x", "xxxyyxx", perl = TRUE, fixed = TRUE)
# engine = "perl"
# engine = "fixed" 
# engine = "default"

str_subset("xxxyz", fixed("."))
str_subset("xxxyz", regex(".", multiline = TRUE))
```

```{r}
str_to_lower()
str_to_sentence()
str_to_upper()
str_to_title()

str_change_case(x, "lower", locale = "en")

str_detect_fixed()
str_detect_regexp()
str_detect_coll()
stringi::stri_replace
```

* Many very simple functions <-> few more complicated functions

* Look independence; orthogonality; Cartesian products; combinatorial explosion - be able to implemnt n approaches to problem A and m approaches to problem B, and n * m solution.

```{r}
df %>% summarise_all(mean)
df %>% summarise_at(vars(starts_with("f")), mean)
df %>% summarise_if(is.numeric, mean)

df %>% summarise(
  across(is.numeric, mean),
  across(is.factor, nlevels),
  n = n()
)
df %>% summarise(
  across(is.numeric & starts_with("f"), mean)
)
df %>% summarise(
  rowMeans(across(is.numeric))
)
```


## Hidden arguments

```{r}
str(data.frame(x = "abc"))
options(stringsAsFactors = FALSE)
str(data.frame(x = "abc"))

str_to_lower("I", locale = "tr")
str_to_upper("i", locale = "tr")
str_to_upper("i", locale = "tr")
# Statİdentity

sort(letters)

str_sort(c("a", "o", "z", "å", "ø"))
str_sort(c("a", "o", "z", "å", "ø"), locale = "se")

print(1.23)
options(OutDec = ",")
print(1.23)
```

```{r}
library(purrr)
x <- list(list(a = 1), list(a = 2), list(b = 3))

map_dbl(x, "a", .default = NA)
map_dbl(x, pluck("x"))
map_dbl(x, function(x, ...) x$a, .default = NA)
```


