# Object-oriented programming

* Base types - `typeof()`
* S3 - simplest system of OOP. Adding attributes to an object.
  The most important attribute `class`
* S4 - robust, but much more complicated, and unless you're working with Bioconductor. Don't use until there's a good book about it.
* R6 - very different to S3/S4, it's much more like OOP in python or javascript, or basically any other popular programming language of the last 20 years (apart from Julia). Powers reticulate. Useful in various places in Shiny. Avoided unless you really need it.

Five chapters: <https://adv-r.hadley.nz>.

## S3

The simplest thing that might possibly work. Built on top of regular R objects (atomic vectors, lists, functions, ...).

```{r}
df <- data.frame()
f <- factor()
mod <- lm(mpg ~ cyl, data = mtcars)

sloop::otype(df)
sloop::otype(f)
sloop::otype(mod)
sloop::otype(1:30)
sloop::otype(tibble::tibble())

typeof(tibble::tibble())
typeof(df)
typeof(f)
typeof(mod)

attributes(df)
attributes(tibble::tibble())
attributes(f)
attributes(mod)
```

```{r}
dt <- tibble::tibble(x = 1)
sloop::s3_dispatch(print(dt))
```

* `print()` is called a **generic function** = interface
* specific function is called **method** = implementation

(F1 = help; F2 = definition)

```{r}
new_foo <- function() {
  x <- list()
  class(x) <- "foo"
  x
}
y <- new_foo()

sloop::s3_dispatch(print(y))

print.foo <- function(x, ...) {
  cat("Hello!\n")
  invisible(x)
}
sloop::s3_dispatch(print(y))
print(y)
y

z <- 1:10
class(z) <- "test"
t(z)
t
sloop::s3_dispatch(t(z))
# calls t.test() 
# because t.test is named like method
# this is why you should never use . in your function names

t
sloop::ftype(t)
```

```{r}
foo <- function(x) x + 1
class(foo) <- "sneaky"
print.sneaky <- function(x, ...) {
  cat("function(x) x + 2\n")
}
foo
foo(1)
```

Another aside:

```{r}
this_function_will_self_destruct <- function() {
  rm(this_function_will_self_destruct, envir = globalenv())
  
  100
}
this_function_will_self_destruct()
this_function_will_self_destruct()
```

More evil:

```{r}
`(` <- function(x) {
  if (is.numeric(x) && runif(1) < 0.01) {
    1
  } else {
    x
  }
}
rm(`(`)
```

