* implementation vs interface
* inside vs outside 

**Your turn**: What are the properties of a function that determine its interface? (There are at least 9)

* Name
* Arguments
  * Names / number
  * `...`
  * Order
  * Types (integer, character, data frames ...)
    (Valid values)
  * Default 
  * Does it use tidy evaluation?
* Output (type)
* Side-effects
  * Throwing an error
  * Prints to console (e.g. progress bar)
  * Plot, save to disk, ...

?grepl

**Your turn**: What are some the problems here?

```{r}
strsplit(x, split, ...)
grep(pattern, x, value = FALSE, ...)
grepl(pattern, x, ...)
sub(pattern, replacement, x, ...)
gsub(pattern, replacement, x, ...)
regexpr(pattern, text, ...)
gregexpr(pattern, text, ...)
regexec(pattern, text, ...)
substr(x, start, stop)
nchar(x, type, ...)
```

* Names
  * based on unix command line tool names
  * who is Greg?
  * some pattern, but not clear? 
    * g = global for gsub, gregexp, but not grep or grepl
  * very concise
  * how do you talk about them?
  
* Arguments
  * order is weird
    * data only comes first in strsplit
  * `x` vs `text`

* Outputs
  * `grep()` depending on the arguments - `value = FASLE` gives positions, `value = TRUE` gives values
  * `regexpr()` can not easily combine with `substr()`
  * `strsplit()` returns a list, even if there are the same number of pieces in every group

* Other
  * important missing functions

## Names

**Your turn**: what are the stringr equivalents of these function?

```{r}
strsplit()  # -> str_split()
grep()      # -> str_which() / str_subset()
grepl()     # -> str_detect()
sub()       # -> str_replace()
gsub()      # -> str_replace_all()
```
```
str_detect() - str_something_lgl()
str_which()  - str_something_int()
str_subset() - str_something_chr()

str_locate_vec()
str_locate_str()

str_to_lower() - str_whisper()
str_to_upper() - str_yell()
```

**Your turn**  What stringr functions don't obey these principles? What other tidyverse functions are bad examples?

```{r}
invert_match() # match_invert()
case
str_detect(words, fixed(".x."))
str_length()
word()
str_c()
```

```{r}
str_to_upper()
str_to_lower()
str_to_title()
str_to_sentence()

str_capitalise(x, to = "upper")
str_capitalise(x, to = "lower")
str_capitalise(x, to = "title")
str_capitalise(x, to = "sentence")
```

### Order

**Your turn**: Can you divide these arguments up into functional groups?

* data: `x` and `text`: required, vectors, primary input

* descriptors: `split`/`pattern`, `replacement`, `start`, `stop`: required, but not the data

* details: `fixed`, `ignore.case`, `perl`, optional/defaults, affect the details of result, single values (not vectorised)

```{r}
strsplit(x, split, fixed = TRUE)
grepl(pattern, x, fixed = TRUE, ignore.case = TRUE)
gsub(pattern, replacement, x, fixed = TRUE, ignore.case = TRUE)
gregexpr(pattern, text, fixed = TRUE)
substr(x, start, stop)
```

* data - use with pipe, never name this argument
  `mean(x = 1:10)` `mean(1:10)`
  `left_join(x, y)`, `lm(y ~ x, data = df)`

* descriptors - 2-3, usually not named 
  `str_replace(x, "pattern", "replacement")`

* dots (...) (if you're using them)

* details
  `mean(1:10, , TRUE)`

### Names

```{r}
x %>% 
  grepl("pattern", .)
```


* Use a consistent naming scheme
* Nouns
* err on side of being descriptive and long

### Required arguments

**Your turn**: in these functions, which arguments are optional? which are required?

```{r}
y <- 1:5
x <- rnorm(5)
lm(y ~ x)

sample(1:5)

diag(1:10)
diag(nrow = 1)
diag(nrow = 1, ncol = 2)

str_sub()
str_replace_all()

str_replace_all("abc", c(a = "X", b = "Y"))

```

General rule: no default = reqiured. Has default = optional. Never use `missing()`

```{r}
x <- c("bbaaab", "bbb", "bbaaba")
loc <- regexpr("a+", x)
str(loc)

substr(x, loc, loc + attr(loc, "match.length") - 1)
substr(x[[2]], -1, -3)

loc <- str_locate(x, "a+")
str_sub(x, loc[, 1], loc[, 2])

str_sub(x, str_locate(x, "a+"))
str_extract(x, "a+")

str_replace_all(x, "a+", str_to_upper)
```

### Hidden

**Your turn**: when do these functions return different results?

```{r}
data.frame(x = "abc")
tolower("I")
sort(letters)


```

```{r}
data.frame(x = "abc")
options(stringsAsFactors = FALSE)
data.frame(x = "abc")

tolower("I")
str_to_lower("I", "tr")

geom_point(stat = "identity")
"identity" -> StatIdentity
str_to_upper("i", locale = "tr")

toupper()

str_sort(c("a", "o", "z", "å", "ø"))
str_sort(c("a", "o", "z", "å", "ø"), locale = "se")

Sys.time()
```

<https://www.vice.com/en_us/article/zmjwda/a-code-glitch-may-have-caused-errors-in-more-than-100-published-studies>

## Output

`str_sub(x, start, end)`:

* is always a character vector
* `length()` is always the same as `max(length(x), length(start), length(end))`

```{r}
x <- str_sub(c("xy", "x2", "21"), 1, 1)
str_sub("Hadley", 1:5, -1)
str_sub(c("Hadley", "Jenny"), 1:5, -1)
```

`str_detect(x, pattern)`:

* logical vector
* `length(str_detect(x))` equals `length(x)`

**Your turn** What invariants do `grep()` and `str_which()` have?

`grep()`
* integer or double or character 
* `length(grep(x))` <= `length(x)`

`str_which()`
* integer vector
* 

`str_which()`:


**Your turn**: Are these consistent? What do these results say about the invariants?  

Back at 1:30pm

```{r}
x <- c(NA, "", "x", "y", "yy")

# character(), length(x)
str_extract(x, "y")
str_extract(x, "y*")

# list(), length(x)
# character vector, length is number of matches
str(str_extract_all(x, "y"))

str_locate(x, "y")
str_locate(x, "y*")
# [)
str_locate_all(x, "y")

str_match_all(x, "(y)")

str_split(x, "x")
str_match(x, "(y)")
str_split_fixed(x, "x", 2)
```

