# Types

```{r}
y <- sum(x)
```

**Your turn**: What can you tell me about x and y? (assuming this code runs)

* `x`: a logical, numeric (integer/double)
* `y`: numeric, length 1

`sum(c(x, y))` equals `sum(x)` + `sum(y)`
`sum(c(numeric(), 5))` equals `sum(numeric())` + `sum(5)`
`5` equals = 0 + 5

**Your turn**: What can you tell me about x and y? (assuming this code runs)

```{r}
y <- sapply(x, f)
```

* `x`: vector (logical, numeric, character, list)
* `y`: ???

```{r}
y <- vapply(x, f, numeric(1))
```

* `x`: vector
* `y`: numeric vector of length `length(x)`

```{r}
y <- map_dbl(x, f)
```

### Vector types

**Your turn**: Eight important vector types in base R: What are they?

* logical
* numeric (integer & double)
* character
* factors (ordered)
* lists
* dates (Date)
* date-times (POSIXct)
* duration (difftime)

* matrices
* complex
* expression

**Your turn**: What is the type of these functions?

* `sum()`: logical | numeric -> numeric[1]

* `mean()`: logical | numeric -> numeric[1]; date | date-time -> date-time[1]

* `dplyr::first()` vector -> same type of vector [1]

* `paste()` (with collapse argument set): vector -> character [1]

* `sqrt()` logical, numeric -> numeric; output same length as input

* `pmin()`: both the same type -> that type back; different types are complicated (`pmin()` and `<` and `min()` and `order()` (`sort()`) should be consistent, `median()`?)

Challenge: what about the sizes?

```{r}
1:3 + 1
1:4 + 1:2
1:4 + 1:3

data.frame(x = 1:4, y = 1:3)
pmin(1:3, 1:2)
cbind(1:3, 1:2)
1:3 + 1:2

dplyr::mutate(data.frame(x = 1:3), y = 1)
dplyr::mutate(data.frame(x = 1:3), y = 1:2)

filter(df, x > 1)
```

```{r}
col_mean <- function(df) {
  num <- sapply(df, is.numeric)
  sapply(df[, num], mean)
}

col_mean(mtcars)
col_mean(iris)

col_mean(mean)
col_mean(1:10)

col_mean(data.frame(x = 1:10))
col_mean(data.frame(x = "a"))


col_mean2 <- function(df) {
  num <- vapply(df, is.numeric, logical(1))
  vapply(df[, num, drop = FALSE], mean, numeric(1))
}

col_mean2(mean)
col_mean2(1:10)

col_mean2(data.frame(x = 1:10))
col_mean2(data.frame(x = "a"))
```

## vctrs

```{r}
library(vctrs)

vec_ptype(letters)
vec_ptype(Sys.Date())
```
```{r}
vec_ptype_show(letters)
vec_ptype_show(Sys.Date())

letters[0]

f <- factor(c("a", "a", "b"))
f
vec_ptype(f)

vec_ptype_show(Sys.time())

now <- Sys.time()
vec_ptype_show(now)
vec_ptype_show(now - (now + 3600 * 100))
```

**your turn**: What is the prototype of a data frame?

```{r}
str(vec_ptype(mtcars))
str(mtcars[0, ])

vec_ptype_show(iris)
```

```{r}
vec_ptype_show(vec_rbind(
  tibble(x = 1, y = factor("a")),
  tibble(x = 2, y = factor("b"))
))
```

## S3 vector

* logical
* numeric (integer & double)
* character
* lists

* factors (ordered)
* dates (Date)
* date-times (POSIXct)
* duration (difftime)

```{r}
f <- factor("x")
typeof(f)
attributes(f)

```
**Your turn** Determine the underlying base type and the attributes for dates and date-times

```{r}
typeof(Sys.Date())
attributes(Sys.Date())

typeof(Sys.time())
attributes(lubridate::now())
```

```{r}
vec_data(Sys.Date())
Sys.Date() + 2
vec_data(Sys.Date() + 2)
new_date(5000)

vec_data(Sys.time())
new_datetime(0, tz = "UTC")
```

```{r}
f <- factor(letters)
f
class(f)
class(f) <- "Date"
f
```

## Back at 3:30pm

## Generics

```{r}
library(sloop)
ftype(mean)
ftype(sum)

s3_dispatch(print(ordered(1:3)))
s3_get_method(print.factor)

ftype(mean)
s3_dispatch(mean(Sys.Date()))
s3_get_method(mean.Date)
```

We're focussing on vectors - 

```{r}
mod <- lm(mpg ~ disp, data = mtcars)
typeof(mod)
attributes(mod)
str(mod)

s3_dispatch(print(mod))
s3_get_method(print.lm)

length(mod)
data.frame(x = 1:12, mod = mod)
tibble(x = 1:12, mod = mod) # bad tibble
```

### Creating a new generic

`bizarro()`: 
* `vec_ptype(bizarro(x))` equal `vec_ptype(x)`
* `length(bizarro(x))` equals `length(x)`
* `bizarro(bizzaro(x))` equals `x`

```{r}
bizarro("abc")
#> cba

bizarro(1)
#> -1

bizarro(c(TRUE, FALSE))
#> FALSE TRUE
```

```{r}
bizarro <- function(x) {
  if (is.character(x)) {
    str_reverse(x)
  } else if (is.numeric(x)) {
    -x
  } else if (is.logical(x)) {
    !x
  } else {
    stop("Don't know how to bizarro a ", class(x)[[1]])
  }
}
```


### Generics and types

```{r}
mean2 <- function(x, na.rm = TRUE) {
  UseMethod("mean2")
}
```

Invariants of mean:
* output is always of length 1

**Your turn** What type of output should you get? (maybe it shouldn't allowed, and you should error)

  logical   -> numeric
  numeric   -> numeric
  date      -> date-time (hint: convert to a date time)
  date-time -> date-time
  duration  -> duration
  list      -> error
  character -> error
  factor    -> error
  ordered   -> error
  ??? ->       error
  
**Your turn**: Make a mean2 generic and implement as many methods as you can in 10 minutes.

```{r}
mean.numeric <- function(x, ..., na.rm = TRUE) {
  
}

weighted.mean(c(1, 10), wt = c(10, 0))
weighted.mean(c(1, 10), w = c(10, 0))
```

## Motivation

WAT

```{r}
f1 <- factor("a")
f2 <- factor("b")
c(f1, f2)
vec_c(f1, f2)

today <- as.Date("2019-10-15")
lunch <- as.POSIXct("2019-10-15 12:30")
c(today, lunch)
c(lunch, today)

vec_data(c(today, lunch))
vec_data(today)
vec_data(lunch)

# vec_ptype(vec_c(x, y)) equal vec_ptype(vec_c(y, x))
vec_c(today, lunch)
vec_c(lunch, today)

lunch_nz <- as.POSIXct("2019-10-15 12:30", tz = "Pacific/Auckland")
lunch
attributes(lunch)
vec_c(lunch, lunch_nz)
vec_c(lunch_nz, lunch)

lunch_nz
attributes(c(lunch_nz))

c(lunch_nz, f1)
c(f1, lunch_nz)
vec_c(f1, lunch_nz)

```




```{r}
d1 <- new_duration(10, "sec")
vec_data(d1)
d2 <- new_duration(10, "hours")
vec_data(d2)

mean(c(d1, d2))
```



<https://bit.ly/2Ml2h8x>
