# Types

```{r}
y <- sum(x)
```

**Your turn**: What can you tell me about x and y? (assuming this code runs)

* `x`: a logical, numeric (integer/double)
* `y`: numeric, length 1

`sum(c(x, y))` equals `sum(x)` + `sum(y)`
`sum(c(numeric(), 5))` equals `sum(numeric())` + `sum(5)`
`5` equals = 0 + 5

**Your turn**: What can you tell me about x and y? (assuming this code runs)

```{r}
y <- sapply(x, f)
```

* `x`: vector (logical, numeric, character, list)
* `y`: ???

```{r}
y <- vapply(x, f, numeric(1))
```

* `x`: vector
* `y`: numeric vector of length `length(x)`

```{r}
y <- map_dbl(x, f)
```

### Vector types

**Your turn**: Eight important vector types in base R: What are they?

* logical
* numeric (integer & double)
* character
* factors (ordered)
* lists
* dates (Date)
* date-times (POSIXct)
* duration (difftime)

* matrices
* complex
* expression

**Your turn**: What is the type of these functions?

* `sum()`: logical | numeric -> numeric[1]

* `mean()`: logical | numeric -> numeric[1]; date | date-time -> date-time[1]

* `dplyr::first()` vector -> same type of vector [1]

* `paste()` (with collapse argument set): vector -> character [1]

* `sqrt()` logical, numeric -> numeric; output same length as input

* `pmin()`: both the same type -> that type back; different types are complicated (`pmin()` and `<` and `min()` and `order()` (`sort()`) should be consistent, `median()`?)

Challenge: what about the sizes?

```{r}
1:3 + 1
1:4 + 1:2
1:4 + 1:3

data.frame(x = 1:4, y = 1:3)
pmin(1:3, 1:2)
cbind(1:3, 1:2)
1:3 + 1:2

dplyr::mutate(data.frame(x = 1:3), y = 1)
dplyr::mutate(data.frame(x = 1:3), y = 1:2)

filter(df, x > 1)
```

```{r}
col_mean <- function(df) {
  num <- sapply(df, is.numeric)
  sapply(df[, num], mean)
}

col_mean(mtcars)
col_mean(iris)

col_mean(mean)
col_mean(1:10)

col_mean(data.frame(x = 1:10))
col_mean(data.frame(x = "a"))


col_mean2 <- function(df) {
  num <- vapply(df, is.numeric, logical(1))
  vapply(df[, num, drop = FALSE], mean, numeric(1))
}

col_mean2(mean)
col_mean2(1:10)

col_mean2(data.frame(x = 1:10))
col_mean2(data.frame(x = "a"))
```

## vctrs

```{r}
library(vctrs)

vec_ptype(letters)
vec_ptype(Sys.Date())
```
```{r}
vec_ptype_show(letters)
vec_ptype_show(Sys.Date())

letters[0]

f <- factor(c("a", "a", "b"))
f
vec_ptype(f)

vec_ptype_show(Sys.time())

now <- Sys.time()
vec_ptype_show(now)
vec_ptype_show(now - (now + 3600 * 100))
```

**your turn**: What is the prototype of a data frame?

```{r}
str(vec_ptype(mtcars))
str(mtcars[0, ])

vec_ptype_show(iris)
```

```{r}
vec_ptype_show(vec_rbind(
  tibble(x = 1, y = factor("a")),
  tibble(x = 2, y = factor("b"))
))
```

## S3 vector

* logical
* numeric (integer & double)
* character
* lists

* factors (ordered)
* dates (Date)
* date-times (POSIXct)
* duration (difftime)

```{r}
f <- factor("x")
typeof(f)
attributes(f)

```
**Your turn** Determine the underlying base type and the attributes for dates and date-times

```{r}
typeof(Sys.Date())
attributes(Sys.Date())

typeof(Sys.time())
attributes(lubridate::now())
```

```{r}
vec_data(Sys.Date())
Sys.Date() + 2
vec_data(Sys.Date() + 2)
new_date(5000)

vec_data(Sys.time())
new_datetime(0, tz = "UTC")
```

```{r}
f <- factor(letters)
f
class(f)
class(f) <- "Date"
f
```

## Back at 3:30pm
