# Tidyverse in packages

* How to refer to functions (recap)
* Tidy evaluation
* Should you use the pipe?

Inspired by <https://ggplot2.tidyverse.org/dev/articles/ggplot2-in-packages.html>, thanks to [Dewey Dunnington](http://github.com/paleolimbot). I'm going to focus on ggplot2, with a dash of dplyr, but the same principles apply to basically any function in the tidyverse.

```{r setup}
library(tidyverse)
```

## Referring to functions

To recap: I think you should start with this:

```{r}
mtcars_summary <- function() {
  ggplot2::ggplot(mtcars) + 
    ggplot2::geom_bar(ggplot2::aes(cyl)) + 
    ggplot2::coord_flip()
}
```

And only change to:

```{r}
#' @importFrom ggplot2 ggplot aes geom_bar coord_flip
mpg_drv_summary <- function() {
  ggplot(mtcars) + 
    geom_bar(aes(cyl)) + 
    coord_flip()
}
```

**NEVER DO THIS**:

```{r}
#' @import ggplot2
mpg_drv_summary <- function() {
  ggplot(mtcars) + 
    geom_bar(aes(cyl)) + 
    coord_flip()
}
```

Because ggplot2 isn't designed with this usage in mind, so it's likely to create conflicts in the future)

**Your turn**: put the above function in a package and check it:

* `usethis::create_package("ggplot2test")`
* `usethis::use_mit_license()`
* `usethis::use_r("summary")`
* `devtools::check()`

What problem does R CMD check uncover? How do you fix it?

## Intro to tidy evalation?

### What is it?

**Your turn**

The following function calls use variables `bins`, `diamonds`, `carat`, `price`, `color`, and `clarity`. In this code, they're all used in the same way. But there's really two types here. What are they? What's the difference?

```{r}
bins <- 50
diamonds %>% 
  ggplot(aes(carat, price)) + 
  geom_hex(bins = bin)
diamonds %>% 
  group_by(color, clarity) %>% 
  summarise(price = mean(price))
```

---

At its heart tidyeval blurs the line between variables in an environment and variables in a data frame. These are deceptively similar because we use the same word for them. One reason that tidy eval is hard is that you have to start to separate these two concepts in your brain (and the point of the tidyverse is so that you don't have to).

```{r}
a <- 1
df <- data.frame(b = 1)

mutate(df, c = a + b)
ggplot(df, aes(a, b)) + geom_point()
```

This blurring makes for elegant data analysis code but causes two problems:

* `R CMD check` can't find df-vars in the environment, so complains
* It's hard to use indirection; i.e. storing a df-var in an env-var

Tidy evaluation is implemented by the rlang package, primarily through `enquo()` and `eval_tidy()`. We're not going to talk about the underlying theory today. I think it's beautiful and elegant and wonderful. Instead we're going to focus on the practicalties.

### `R CMD check`

The first problem you'll encounter when using tidy evaluation in packages is that `R CMD check` reports that the data frame variables you use don't have visible bindings. This is true! But it's not important because `aes()` isn't looking in the environment; `R CMD check` doesn't know that.

* `use_package("~/desktop/tiddlyeval")`
* `use_mit_license()`
* `use_r("ggplot")`

```{r}
#' Diamonds summary
#' 
#' @export
diamonds_summary <- function() {
  diamonds %>% 
    dplyr::group_by(color, clarity) %>% 
    dplyr::summarise(price = mean(price))
}
```

```
N  checking R code for possible problems (2.7s)
   mpg_drv_summary: no visible binding for global variable ‘cyl’
   Undefined global functions or variables:
     cyl
```

One general way to silence this problem is to use `globalVariables()`:

```{r}
globalVariables("cyl")
```

<https://stackoverflow.com/questions/9439256>

But for tidyeval there's a slightly better way that clarifies the intent of your code a little:

```{r}
#' Diamonds summary
#' 
#' @export
#' @importFrom rlang .data
diamonds_summary2 <- function() {
  diamonds %>% 
    dplyr::group_by(.data$color, .data$clarity) %>% 
    dplyr::summarise(price = mean(.data$price))
}
```

This removes the ambiguity about whether `cyl` is in the data or the environment. It only works in functions that use tidy evaluation.

Note that you'll need to `use_package("rlang")` but this doesn't actually increase the dependencies of your package.

---

**Your turn**: Add this function and get R CMD check passing:

```{r}
#' @export
#' @importFrom rlang .data
diamonds_summary2 <- function(bins) {
  diamonds %>% 
    ggplot2::ggplot(aes(carat, price)) + 
    ggplot2::geom_hex(bins = bin)
}
```

## What if you want to use it yourself?

First approach is to avoid it. Pass in the object that `aes()` creates:

```{r}
piechart <- function(data, mapping) {
  ggplot(data, mapping) +
    geom_bar(width = 1) + 
    coord_polar(theta = "y") + 
    xlab(NULL) + 
    ylab(NULL)
}
```

`...` doesn't need any special treatment. This is often the easiest place to start: 

```{r}
count <- function(df, ...) {
  df %>%
    group_by(...) %>% 
    summarise(n = n()) %>% 
    ungroup()
}
```

Trying to send `...` to two different places is often a sign you're trying to be too complicated. Create functions like existing ggplot2 and dplyr functions; small components that you join together.

Don't forget about existing `_if` and `_at` functions in dplyr. They'll take care of a lot of details for you.

### Taking variables as inputs

Two options:

*   Variable name as string

    ```{r}
    col_summary <- function(df, col) {
      ggplot(df) + 
        geom_bar(aes(x = .data[[col]])) + 
        coord_flip() + 
        xlab(col)
    }
    col_summary(mtcars, "cyl")
    ```

*   "Unquoted" variable name + embracing

    ```{r}
    col_summary <- function(df, col) {
      ggplot(df) + 
        geom_bar(aes(x = {{ col }})) + 
        coord_flip()
    }
    col_summary(mtcars, cyl)
    ```

    Inspired by the very awesome glue package:
    
    ```{r}
    name <- "Hadley"
    glue::glue("Hello {name}!")
    ```

**Your turn**: Generalise these functions:

```{r}
# data frame
# any number of groups
# which variable to summarise
diamonds_summary2 <- function() {
  diamonds %>% 
    dplyr::group_by(.data$color, .data$clarity) %>% 
    dplyr::summarise(price = mean(.data$price))
}

# x and y variables
diamonds_summary2 <- function(bins) {
  diamonds %>% 
    ggplot2::ggplot(aes(carat, price)) + 
    ggplot2::geom_hex(bins = bin)
}
```

### Reducing duplication

```{r}
diamonds %>% 
  group_by(color) %>% 
  summarise(price = mean(price))
diamonds %>% 
  group_by(clarity) %>% 
  summarise(price = mean(price))
diamonds %>% 
  group_by(cut) %>% 
  summarise(price = mean(price))
```

Now rather than referring to the column directly, you want to refer to it indirectly - you want to tell `group_by` to group by the varible recorded in `by`, not literally group by the variable called `by`.

```{r}
mean_price <- function(df, by) {
  diamonds %>% 
    group_by(by) %>% 
    summarise(price = mean(price))
}
diamonds %>% mean_price(by = cut)
```

Fixing this problem requires two steps:

1. Identify that it's a tidyeval problem; i.e. you're trying to refer to
   a data frame variable that's stored in a function argument; and you're
   inside the tidyverse

2. Know about embracing `{{ }}`

**Your turn** Reduce the duplication by making a function! 

---

```{r}
mean_price <- function(df, by) {
  diamonds %>% 
    group_by({{ by }}) %>% 
    summarise(price = mean(price))
}
diamonds %>% mean_price(by = cut)
diamonds %>% mean_price(by = color)
```

### Select functions

Some functions have "select" semantics - you don't give them operations that work with values, but operations that work with column names:

* `select()`
* `group_by_at()`
* most tidyr functions

Slighty different options:

* Variables by you: `select(df, one_of("age", "height"))`
* Variables as string: `select(df, one_of(vars))`
* Variables unquoted: `select(df, {{ vars }})`

## The pipe

What if you want to use the pipe in your package? Is it ok?

**Your turn**: 
* What's the cost of dependending on magrittr?
* What's the cost of using the pipe?

---

* no dependencies or system dependenices
* takes max 10s to install
* package is ~180 kb

* `%>%` makes debugging a little harder
* not everyone can understand it
* some performance cost

---

If it works I think you should use it. Most of the packages I work on don't use it, because it doesn't help. But some do! (e.g pkgdown)

If you need to use it usethis is your friend: `usethis::use_pipe()`.
